Due to the nature of this project, the team will only be working on software and will not need access to any labs. The team does conduct weekly meetings in the university's group study rooms and the specific policy is listed below.

\subsection{University Group Study Room Policy}
\subsubsection{Description}
All group study room users must conform to the University's policies for personal conduct: Visitor Conduct Policy. Damage to equipment in the rooms will result in the loss of the ability to reserve and/or occupy any of these rooms. Noise levels from any conversations and/or equipment must not disturb others. All group study room users are expected to be courteous and leave the room ready for the next group. Unattended personal property may not be used to "hold" a room by any individual or group and may be removed by Libraries' staff to allow others to use the space. Staff reserves the right to enter any group study room at any time. Any obstruction to the windows is prohibited. The University and its staff are not responsible for unattended, lost, stolen, or damaged personal items. \cite{UTA}
\subsubsection{Source}
University of Texas - Arlington Group Study Room Policy
\subsubsection{Constraints}
Current UTA students, faculty, and staff may reserve group study rooms with a valid UTA NetID (reserve now). A person may reserve a study room in 30-minute increments up to a maximum of 3 hours per individual per day. Reservations can be made up to 14 days in advance.
% \subsubsection{Standards}

\subsubsection{Priority}
Critical
